\noindent {\bf Chapter editors:}~Juliette Alimena, Martino Borsato, Yangyang Cheng, Monica Verducci\\
\text{ \; }\\
\noindent {\bf Contributors:}~Cristiano Alpigiani, Xabier Cid Vidal, David Curtin, Elena Dall'Occo, Sven Dildick, Jonathan L.~Feng, Iftah Galon, Christopher Hill, Henning Keller, Felix Kling, Simon Knapen, Zhen Liu, Henry Lubatti, Philippe Mermod, Vasiliki A.\ Mitsou, James L.~Pinfold, Jessica Prisciandaro, Dean Robinson, Livia Soffi, Sebastian Trojanowski, Carlos V\'azquez Sierra, Si Xie, Charlie Young\\
\text{ \; }\\

\noindent The experimental searches for LLPs outlined in Chapter~\ref{sec:experimentcoverage} are limited by the abilities of the ATLAS, CMS, and LHCb experiments to trigger on and reconstruct the objects that are associated with each signature. In the Phase 2 high-luminosity upgrade of the LHC (HL-LHC), the extremely high pile-up conditions necessitate the upgrade of all three detectors to maintain triggers at thresholds needed for sensitivity to electroweak, Higgs, and BSM physics (see Refs.~\cite{Schmidt:2016jra,Apollinari:2015bam} for an overview); to reject particles originating from pile-up vertices; and to maintain object reconstruction in the high-luminosity environment. These upgrades include the addition of tracking layers to the forward regions of ATLAS and CMS, improvements to timing reconstruction in events, and the inclusion of tracking information at earlier stages of the trigger (or, in the case of LHCb, the full online reconstruction of every event).

While these upgrades are crucial to the success of the HL-LHC physics goals for conventional searches (such as for electroweak, Higgs, or SUSY signatures), they have the opportunity to be transformative for searches for LLPs. Signatures involving LLPs are often subject to small-to-negligible irreducible backgrounds, and improvements to the reconstruction, timing, and vertexing of displaced objects can typically suppress any instrumental or fake backgrounds. (See Chapter~\ref{sec:backgrounds} for a discussion of sources of backgrounds for LLP searches.) At the same time, the introduction of tracking information to earlier stages of the trigger could be used to trigger on events that may contain hadronically decaying LLPs that must otherwise pass jet triggers, leading to an improvement in sensitivity to low-mass LLPs. Indeed, many of the gaps in coverage from current searches identified in Section~\ref{sec:covgaps} can be closed or reduced using the new technology from detector upgrades. Even more uniquely, LLP signatures may themselves motivate the introduction of new detector elements that are dedicated to exploring new lifetime frontiers in particle physics.

This chapter summarizes current and proposed plans for detector upgrades for the HL-LHC, paying special attention to those features of the detector upgrades that are most relevant for LLP searches. Where available, we show the results of projections for the sensitivity to various LLP scenarios of different improvements to the detector. We also highlight LLP studies for the Phase 2 upgrades that are not yet publicly available that should be done in order to assess (and, where possible, improve) the sensitivity of planned upgrades to LLP signatures. Finally, we include contributions from a number of existing and proposed experimental collaborations whose primary purposes are to search for LLPs produced at LHC interaction points using additional, dedicated detectors. These detectors complement the capabilities of ATLAS, CMS, and LHCb, allowing sensitivity to signatures that are otherwise not possible to reconstruct at the main detectors.

In Section~\ref{sec:upgradelhc}, we combine the discussions of the planned ATLAS and CMS upgrades, facilitating for each detector component a direct comparison between the features of the upgraded detectors of both ATLAS and CMS. Since LHCb has a very different geometry and physics program from ATLAS and CMS, we have a separate discussion of planned LHCb upgrades in Section~\ref{sec:LHCb_upgrade}. Finally, we present the contributions of the dedicated LLP experiments in Section~\ref{sec:dedicated}.

\input{tex/triggers_and_upgrades_ATLAS_CMS.tex}
\input{tex/triggers_and_upgrades_LHCb.tex}
\input{tex/triggers_and_upgrades_dedicated.tex}
